caDDS: Community Assisted Distributed Database for Sequences

### 2020-06-24 Paper2020ACM/Paper2020.tex
June 24 2pm

(Not yet serious) Our advisers have really helped us over the school year. The dificult pandemic has changed our thesis to the point it has been - Cid
\end{acks}

>>>>

We want to acknowledge our advisers for giving the idea for out thesis. And for answering our many questions about genomics. Writing this paper overlapped with the covid19 pandemic which changed a big portion of the scope of this thesis. We thank our advisers for making this work manageable during this pandemic crisis.
\end{acks}
